Supplement

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}

@@

>>>>

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}
\newpage

@@

## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )
